---
title: "ST 558 - Project 2"
author: "Yi Ren and Paula Bailey"
date: "2022-09-22"
---


  * This document will walk the user through the process of connecting to & collecting data from the [pokemon API](https://pokeapi.co/) within R.

## Reference to Render Code
```{r, Render, eval=FALSE}
rmarkdown::render("Project2.Rmd", "github_document","README.md")
```


## Packages for Vignette

  * The following packages are required for connecting and retrieving data from the API.

1. `httr` - Retrieves Data from an API
2. `jsonlite` - Parses Results from an API Query
3. `dplyr` - A part of the `tidyverse` used for manipulating data
4. `tidyr` - A part of the `tidyverse` used for data cleaning
4. `ggplot2` - A part of the `tidyverse` used for creating graphics

```{r libraries, message=FALSE, warning=FALSE}
# Read in Required Packages 
library(httr)
library(jsonlite)
library(tidyverse)
library(ggplot2)

```

  
  
  
  



## 6. Function for moves information
```{r getmoves}
get_moves <- function(type){
  base<-"https://pokeapi.co/api/v2/move/"
  url<-(paste0(base,type,"/"))
  move_api<-GET(url) %>% content("text") %>% fromJSON(flatten=TRUE)
  moves <- tibble(idMove =move_api[["id"]],
  nameMove=move_api[["name"]],
  accuracy = move_api[["accuracy"]],
  power = move_api[["power"]],
  PowerPoint = move_api[["pp"]])
  return(moves)
}
```


## 7. Function to get your pokemon
```{r getpokemon}
get_pokemon <- function(pokemon = 132, tran =1, stat = 1, move = 1, berry=0){
    poke_One<-NULL
    
  if (is.numeric(pokemon) == "TRUE"){
    pokemon_mini<-lookname(lookid(pokemon))
  } else {
    pokemon_mini<-lookname(pokemon)
  }

  poke_One<-NULL  
  if(move == 0 & tran == 1 & stat == 0){
    basic <-basic(pokemon_mini)                  
    traning<-traning(pokemon_mini)
    poke_One<-merge(basic,traning)
  }else if(move == 0 & tran == 0 & stat == 1){
    basic <-basic(pokemon_mini)         
    stat<-stats(pokemon_mini)                   
    poke_One<-merge(basic,stat)
  }else if(move == 1 & tran == 1 & stat == 1){
    poke_One[1]<-lapply(pokemon, FUN=info)      
  }else{
    poke_One[1]<-lapply(pokemon, FUN=info)   
  }
   
  if(berry == 1){
    berry <- get_berry()
  }

return(list(poke_One, berry))
}
```





## Function for berries
  * This function does not require any input arguments. The function loops through the pokemon api and pulls the information for the 64 berries. There is not a direct link to pokemon data itself. It will be used for future analytical purposes.  
```{r getberry}
get_berry <-function(){
  api_json<-GET("https://pokeapi.co/api/v2/berry/1/") %>% content("text") %>% fromJSON(flatten=TRUE)
  berries_df <- as.data.frame(api_json)
  for(i in 2:64){
    base <- "https://pokeapi.co/api/v2/berry/"
    call_next <- (paste0(base,i,"/"))
    api_json2 <- GET(call_next) %>% content("text") %>% fromJSON(flatten=TRUE)
    next_df <- as.data.frame(api_json2)
    berries_df <- rbind(berries_df,next_df)
  }
    berries_df <<-berries_df %>% 
                select(- firmness.url,-flavors.flavor.url,-item.url, -natural_gift_type.url )
}
```










## Get Pokemon
To request information from the api, the user has 3 options:

  1. Get Basic information and Training
  2. Get Basic information and Stats
  3. Get All - Basic information, Training, and Stats
  4. Get Berry information.
  
The default arguments are (pokemon = 132, tran = 1, stat = 1, move = 1, berry=0), where 1 is return this information and 0 do not return this information.   #change EVAL later
```{r onePokemon, eval=FALSE}
get_pokemon("DITTO")
```

```{r test, eval=FALSE}
get_pokemon(18, tran = 1, stat = 0, move = 0, berry=0)
```


```{r test2, eval=FALSE}
get_pokemon(132, tran = 0, stat = 1, move = 0, berry = 0)
```


## Berries subset
```{r berry}
get_berry()
```






## Scatter plot
```{r berscatter}
ggplot(berries_df,aes(x = growth_time, y = soil_dryness)) + 
  geom_smooth(formula = y~x, method = "loess") + geom_point() + 
  labs(x = "Growth Time", y= "Soil Dryness",title = "Impact of Soil Dryness on Growth") +
  theme(legend.title = element_text(size = 6), legend.text = element_text(size = 6), plot.title = element_text(hjust = 0.5))
```


  * This scatter plot shows the relationship between berry growth and soil dryness.  It visually verifies the negative relationship between the growth of berries and soil dryness. As the berry grows, the soil becomes drier.
  
    * This negative relationship is also confirmed in the correlation score of -.68.
```{r}
cor(berries_df$growth_time,berries_df$soil_dryness)
```


```{r, bmi, eval=FALSE}
ggplot(sep, aes(x = round((weight/height),2), y = speed)) +
    geom_point(aes(color = main.type)) +
    labs(x = "BMI", y= "Speed",title = "Body Mass Index (BMI) and Speed") +
    theme(legend.title = element_text(size = 5), legend.text = element_text(size = 5))
```

  * This scatter plot shows the relationship between BMI (weight/height) and speed. We used type of pokemon to highlight the color. This chart shows no clear relationship between a higher BMI and moving at slower speeds. We can see a few pokemon to the right with BMIs around 50; However, they are not the slowest pokemon. 



2. Numeric summaries for berries
```{r berrySummary}
berrySummary <- berries_df %>% select(growth_time, max_harvest, size, smoothness, soil_dryness) %>% apply(2, function(x){summary(x[!is.na(x)])}) 
knitr::kable(berrySummary, caption = 'Summary of Berry Stats', digits = 2)
```

The summary statistics for growth time, maximum harvest, size, smoothness, and soil dryness.  

  * Growth Time : The difference between the mean (12.86) and median (15.00) is small, so we can infer HP is symmetrically distributed and slightly skewed to the left.  Median is higher than mean.
  
  * For Maximum Harvest and  Smoothness, the difference between their respective mean and median is small, so we can infer the shape is symmetrically distributed; however, slightly skewed to the right. The mean is higher than median. 
  
  * For Size and Soil Dryness, the difference between each respective mean and median is relatively large. Since the mean is greater than the median,  we can infer the shape is right skewed.  









  
